Project Glass 2.0 -- Interaction with Physical Devices through Attention

### 2013-05-18 doc/report/conclusion.tex
adding files to the report
added some texts to the report, and a glass FSM figure
update conclusion

\section{Related Work}
\label{sec:related-work}

>>>>

\section{Conclusion}
\label{sec:conclusion}

In this project, we explored a novel way of interacting with physical devices by capturing user's attention. The prototype we built demonstrates the possibility of identifying user's line of sight to select and control target appliances. Furthermore, we designed a mechanism to intuitively choose from multiple targets when they are close-by.

There are still a few more components that require enhancement: (A) Thorough verifications of the IR strength, angles, and reflecting effects. (B) A more robust communication protocol with better error handling. (C) A more stable and richer input method. (D) User study.
